Data-Driven Search-based Software Engineering

### 2018-01-29 doc/tex/msr18/main.tex

\begin{abstract}
This paper introduces Data-Driven Search-based Software Engineering (DSE) which combines insights from Software Analytics (SA) and Search-based Software Engineering (SBSE).  We argue that  
combining these two fields
is useful for (a)~situations which require learning from a large data
source or (b)~when optimizers need to know the lay of the land in order to find better solutions, faster

This paper also presents a  resource (tiny.cc/sbse) for exploring
Data-Driven Search-based Software Engineering.  The resource contains 89 artifacts related to data-driven search-based SE,
divided into 13 groups such as requirements engineering, software product lines, software processes, etc.
All the materials in this repository
have been   used in recent SE papers; i.e. for all this material, there exists baseline results against which researchers can use to comparatively assess their own new ideas

@@

\maketitle
\pagestyle{plain}
% \input{samplebody-conf}

@@

The MSR  community has benefited enormously from widely shared datasets.  Such datasets document the canonical problems in a field.
They serve to cluster together like-minded researchers while  
  allowing   them to generate reproducible results. Also, such data can be used by
   newcomers to learn state-of-the-art methods in this field. Further, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
At the time of this writing,   nine of the 50 most cited papers in the last 5 years at IEEE Transactions of Software Engineering \vivek{all draw their case studies
from a small number of open defect prediction datasets} 
% \TODO{I'm not sure if it is good to say ``a small number of similar datasets''. What about saying that they all draw their case studies from open datasets?}.

As a field evolves, so too should its canonical problems. One  reason for the emergence of   MSR  in 2004 was the existence of a new generation of widely-available data mining
algorithms that could scale to interestingly large problems.  Now, some 14 years later, a new technology has emerged that could reshape the future of this community \TODO{I wouldn't say that SBSE emerged in 2017/18! There is work in this area since the 90s, plus some isolated earlier works.}. There now exists numerous, readily
available, {\em search-based software engineering} (SBSE) algorithms. Whereas:
\begin{itemize}
\item
An MSR researcher might deploy a
data miner to learn a model from  data   that predicts for (say) a single target class;
\item
An SBSE researcher might deploy a multi-objective optimizer
to find what \llm{solutions} score best
on multiple target variables.
\end{itemize}

\llm{In other words, both MSR and SBSE share the common goal of providing insights to improve software engineering. However, MSR formulates software engineering problems as data mining problems, whereas SBSE formulates software engineering problems as (frequently multi-objective) optimization problems.}

@@

\llm{The similar goals of these two areas, as well as the intrinsic relationship between data mining and optimization algorithms, has been recently inspiring an} increase in methods that combine MSR and SBSE.
A recent \llm{NII Shonan Meeting}  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) mining software repositories can be improved using \llm{tools from the SBSE community}; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE \llm{algorithms} can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared  resources 
to help more  researchers and educators   explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/sbse,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
All the materials in this repository
have been   used in recent SE papers; i.e. for all this material, there exists baseline results against which researchers can use to comparatively assess their own new ideas.
%\TODO{Re: fig. 1, are we allowed to use Abhaham's nice piece of art?}

@@

The rest of this paper discusses SBSE and its connection to MSR. 
We offer a ``cheats' guide'' to SBSE with just enough information to help researchers and educators use the artifacts in the resource. More specifically, the contributions of the paper are:
\begin{itemize}
    \item To show that optimization (SBSE) and learning (MSR) goes hand in hand,
    \item Provide resources to seed various research,
    \item Provide teaching resources, which can be used to create DSE courses, and
    \item Based on our experience, various strategies which can be used to make these DSE techniques more efficient.
\end{itemize}

@@

\begin{figure*}
    \centering
\small
\colorbox{gray!10}{
\begin{tabular}{@{}p{3cm}p{6cm}p{8.35cm}@{}}
\multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Problems in Search-based Software Engineering}}} \\ 
\multicolumn{3}{c}{
		\begin{minipage}[b]{0.33\linewidth}
			\begin{flushleft}
				\includegraphics[height=4.5cm]{doc/tex/msr18/img/pareto.png}
				\vspace{8pt}
			\end{flushleft}
		\end{minipage}\hspace{0.1cm}
		\begin{minipage}[b]{0.63\linewidth}
		        \textbf{Problem: } SBSE converts a SE problem into an optimization problem, where the goal is to find the maxima or minima of objective functions \llm{$y_i=f_i(x)$, $1 \leq i \leq m$, where  $f_i$ are the objective / evaluation functions, $m$ is the number of objectives,} x is called the \textit{independent variable}, and $y_i$ are the \textit{dependent variables}.\\
		        %\textbf{Problem Types: } The problems can be either single-~\cite{nair2017faster} or multi-~\cite{chen2017sampling} or many-objective~\cite{mkaouer2014high}.\TODO{We are not telling what the difference between multi- and many- is here. If we need to save space for the figure to fit in one page, we could possibly omit ``many''.}\\
		        \textbf{Global Maximum/Minimum: } For single objective ($m=1$) problems, algorithms aim at finding a single solution able to optimize the objective function, i.e., a global maximum/minimum. \\%there is one global maxima or minima \TODO{This statement is wrong. Single objective problems can have multiple global optima! The difference is that they have only one function to be optimized. I think what you mean here is that, in single objective problems, we are interested in retrieving a single solution able to maximize or minimize the objective function.}.\\
		        \textbf{Pareto Front: } For multi-objective ($m>1$) problems, there is no single `best' solution, but a number of `best' solutions. The best solutions are \llm{non-dominated solutions} found using a \textit{dominance} relation.\\
		        \textbf{Dominance: }The domination criterion  can be defined as: ``A solution $x_1$ is said to dominate\\
                another solution $x_2$, if $x_1$ is no worse than $x_2$ in all objectives
                and $x_1$ is strictly better than $x_2$ in at least one objective.'' A solution is called non-dominated if no other solution dominates it.\\
		        \textbf{Actual \llm{Pareto Front} (PF): } A list of best solutions of a space is called Actual PF ($a\in A$). As this can be unknowable in practice or prohibitively expensive to generate, it is common to take from the union of all optimization outcomes all non-dominated solutions and use it as the (approximated) PF.\\ %This requires knowledge of the whole space---which is not available in real-world setting.\\
		        \textbf{Predicted PF: } The solutions found by \llm{an optimization} algorithm are called the Predicted PF ($p\in P$).
				%  Problems tacked in SBSE can be described as finding the best (minimum or maximum) of a function ($y=f(x)$), where x is called the \textit{independent variable}, $f$ is the evaluation function, and $y$ the \textit{dependent variable}. $y$ can either be single objective or multi-objective. In a multi-objective setting, there no single `best' solution instead there is number of `best' solution. This can also be stated as solutions which are better (or \textit{dominates}) all other solution---which is not considered `best' solutions, and no better than other `best' solution as defined by domination criterion. The domination criterion  can be defined as: ``A solution $x_1$ is said to dominate
    %             another solution $x_2$, if $x_1$ is no worse than $x_2$ in all objectives
    %             and $x_1$ is strictly better than $x_2$ in at least one objective.'' The list of these `best' solutions are called the \textit{Pareto Front}. The figure represents a solution space of a (synthetic) multi-objective problem with two objectives: $\mathit{Objective}_1$ and $\mathit{Objective}_2$. This best point can be called as the \textit{Utopia Point} and the worst is called the \textit{Nadir Point}. The points $A_i$ represents the \textit{Actual Pareto Front} ($A$). The goal of the multi-objective optimizer is to find set of solutions which are closest to the actual Pareto frontier. The solutions found by the optimizers are called the \textit{Predicted Pareto Front} ($P$). \vspace{0.1cm}
		\end{minipage}

} \\ 
\multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Components of Meta-heuristic Algorithms (search-based optimization algorithms such as NSGA-II~\cite{deb2000fast}, SPEA2~\cite{zitzler2001spea2}, MOEA/D~\cite{zhang2007moea}, AGE~\cite{wagner2015age})}}} \\
\multicolumn{3}{c}{
\begin{minipage}[b]{\linewidth}
\vspace{0.1cm}
% \TODO{I'm not sure how useful it is to explain the components here if we don't show the pseudocode of an algorithm, as the persons who don't know the components will not know the pseudocode either, and will thus be unable to understand. Perhaps we can eliminate the plot from the previous section of this figure and add a figure with a general meta-heuristic pseudocode here?}
\begin{wrapfigure}{r}{0.4\textwidth}
\includegraphics[height=4.8cm]{doc/tex/msr18/img/sbse_code.png}
\end{wrapfigure}
\noindent\textbf{Data Collection or Model building: } SBSE process can either rely on a model, which represent a software process~\cite{boehm1995cost} or can be directly applied to any software engineering problem including problems which require evaluating a solution by running a specific benchmark~\cite{krall2015gale}.

\noindent\textbf{Representation: } \llm{This defines how solutions $x$ are represented internally by the algorithm.
Examples of representations are Boolean or numerical vectors, but more complex representations are also possible. The space of all values that can be represented is the} \textit{Decision Space}.
% The representation of these solutions is significant to generate the landscape of the problem.

\noindent\textbf{Population: } A set of solutions maintained by the algorithm using the representation.

\noindent\textbf{Initialization: } The process of search \llm{typically} starts by creating random solutions (valid or invalid)~\cite{saber2017seeding, chen2017beyond, chen2017sampling, henard2015combining}.

\noindent\textbf{Fitness Function: } A fitness function maps the solution (which is represented using numerics) to a numeric scale (also called as \textit{Objective Space}) which is used to distinguish between good and not so good solutions. This measure is a domain-specific measure (single objective) or measures (multi-objective) which is useful for the practitioners.
Simply put fitness function is a transformation function which converts a point in the decision space to the objective space.

\noindent\textbf{Operators: } \llm{These are operators that (1) generate new solutions based on one (e.g., mutation operator) or more (e.g., crossover or recombination operators) existing solutions, and (2) operators that select solutions to pass to the aforementioned operators or to survive for the next iteration of the algorithm. The operators (2) typically apply some pressure towards selecting better solutions either deterministically (e.g., elitism operator) or stochastically.} 
% \TODO{If space allows, we can mention survival of the fittest.} % They can be used along with an}\TODO{I haven't finished this change yet. I have to come back later.} 
\textit{elitism operator} simulates the `survival of the fittest' strategy i.e., eliminates not so good solutions thereby preserving the good solutions in the population.

\noindent\textbf{Generations: } \vivek{A meta-heuristic algorithm iteratively improves the population (set of solutions) iteratively. Each step of this process, which includes generation of new solutions using recombination of the existing population and selecting solutions using the elitism operator, is called a generation.  Over successive generations, the population `evolves' toward an optimal solution.}
\end{minipage}\hspace{0.1cm}
% \begin{minipage}[b]{0.4\linewidth}
% 				\includegraphics[height=4.7cm]{doc/tex/msr18/img/sbse_code.png}
% 				\vspace{1cm}
% \end{minipage}
}
 \\
\multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Performance Measures (Refer to \cite{wang2016practical,chand2015manyemo} for more detail)}}} \\ 
% \multicolumn{2}{c}{\textbf{SA}} & \textbf{SBSE} \\ \midrule
\multicolumn{3}{c}{

\begin{minipage}[b]{0.33\linewidth}
\includegraphics[height=2.8cm]{doc/tex/msr18/img/gd.png}
\includegraphics[height=2.8cm]{doc/tex/msr18/img/igd.png}\\
\includegraphics[height=2.8cm]{doc/tex/msr18/img/hv.png}
\includegraphics[height=2.8cm]{doc/tex/msr18/img/spread.png}

\end{minipage}

\begin{minipage}[b]{0.67\linewidth}
\vspace{0.1cm}
\TODO{I understand the reason why we are only discussing multi-objectives here, but the target audience of this figure may not know. It's worth mentioning sth about single objectives here.}
\noindent\textbf{Generational Distance: } Generational distance is the measure of convergence---how close is the predicted Pareto front is to the actual Pareto front. It is defined to measure (using Euclidean distance) how far are the solutions that exist in $P$ from the nearest solutions in $A$. In ideal case, the GD is 0, which means the predicted PF is a subset of the actual PF. Note that it ignores how well the solutions are actually spread out.

\noindent\textbf{Spread: } Spread is a measure of diversity---how well the solutions in P are spread. An ideal case is when the solutions in P is spread evenly across the Predicted Pareto Front.

\noindent\textbf{Inverted Generational Distance: } Inverted Generational distance measures both convergence as well as diversity of the solutions---measures the shortest distance from each solution in the Actual PF to the closest solution in Predicted PF. Like Generational distance, the distance is measured in Euclidean space. In an ideal case, IGD is 0, which means the predicted PF is same as the actual PF.

\noindent\textbf{Hypervolume: } Hypervolume measures both convergence as well as diversity of the solutions---hypervolume is the union of the cuboids w.r.t. to a reference point. Note that the hypervolume implicitly defines an arbitrary aim of optimization. Also, it is not efficiently computable when the number of dimensions is large, however, approximations exist.

\noindent \textbf{Approximation: } Additive/multiplicative Approximation is an alternative measure which can be computed in linear time (w.r.t. to the number of objectives). It is the multi-objective extension of the concept of approximation encountered in theoretical computer science. 
% The intuition is that the search process aims at finding a set of solutions with a small approximation ratio, so why not simply compute the approximation ratio (as?

\end{minipage}	
}\\
\end{tabular}}
\caption{A \llm{brief} tutorial on Search-based Software Engineering.}
\label{fig:sbse_crash}
\end{figure*}

\begin{figure*}
    \centering
    \begin{tabular}{@{}p{3cm}p{6cm}p{8.35cm}@{}}

                % \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{}}} \\ 
                \rowcolor{gray}\textcolor{white}{\textbf{Features}} & \hspace{2cm}\textcolor{white}{\textbf{MSR}} & \hspace{3cm}\textcolor{white}{\textbf{SBSE}} \\ 
                 \rowcolor{gray!30} \textbf{Primary inference} & Induction, summarization, visualization & Optimization \\
                \textbf{Inference speed} & Very fast, scalable & Becoming faster, more scalable\\
                 \rowcolor{gray!30}\textbf{Data} often collected &
                 Once,  then processed.
                &
                On-demand
                from  some model---which means an SBSE analysis can 
                generate new samples of the data in very  specific regions.
                \\ 
                \textbf{Conclusions} often 
                generated via
                &
                A single  execution of a data miner
                (perhaps with some data pre-processing).\TODO{This is arguable, given the popularity of ensembles.} 
                &
                An evolutionary process  where execution $i+1$ is guided
                by the results of execution $i$.
                \\

                 \rowcolor{gray!30}\textbf{Canonical   tools} are usually
                &
                Data mining algorithms like  the decision
                tree learners of WEKA~\cite{hall2009weka} or the mathematical modeling tools of R~\cite{rmanual18} or Scikit-learn~\cite{scikit-learn}.
                &
                \llm{Search-based} optimization algorithms which may be either home-grown scripts or parts of large toolkits such as jMETAL\cite{refs2jmetalDEE}, Opt4j~\cite{opt4jpaper}, DEAP~\cite{DEAP_JMLR2012}.
                \\ 
                \textbf{Canonical   problems}
                &
                Defect prediction~\cite{lessmann2008benchmarking}   or Stackoverflow text mining~\cite{fu2017easy}. 
                &
                Minimizing a test suite~\cite{fraser2007redundancy}, configuring a software system~\cite{nair2017faster} or extracting a valid products from a product line description~\cite{sayyad13b}.
                % or selecting screen designs that
                % reduce the power consumption  mobile devices
                \\

@@

@@

\begin{figure}[!t]
\small

>>>>

\begin{abstract}
This paper introduces Data-Driven Search-based Software Engineering (DSE) which combines insights from Software Analytics (SA) and Search-based Software Engineering (SBSE). SBSE reformulate the SE problem as an optimization problem and uses a meta-heuristic algorithm to solve those problems. Both the fields, SA and SBSE, are concerned with providing insights for software engineers to improve SE tasks. The similar goals of the two fields are one of the major reasons as to why these two fields should work together. 
We argue that  
combining these two fields
is useful for (a)~situations which require learning from a large data
source or (b)~when optimizers need to know the lay of the land to find better solutions, faster.

This paper also presents a  resource (tiny.cc/sbse) for exploring
Data-Driven Search-based Software Engineering.  The resource contains 89 artifacts related to data-driven search-based SE,
divided into 13 groups such as requirements engineering, software product lines, software processes, etc.
All the materials in this repository
have been   used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas

@@

\maketitle
%\pagestyle{plain}
% \input{samplebody-conf}

@@

The MSR  community has benefited enormously from widely shared datasets.  Such datasets document the canonical problems in a field.
They serve to cluster together like-minded researchers while allowing them to generate reproducible results. Also, such data can be used by
   newcomers to learn state of the art methods in this field. Further, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
At the time of this writing,   nine of the 50 most cited papers in the last 5 years at IEEE Transactions of Software Engineering {all draw their case studies
from a small number of readily available defect prediction datasets} 
% \TODO{I'm not sure if it is good to say ``a small number of similar datasets''. What about saying that they all draw their case studies from open datasets?}.

As a field evolves, so too should its canonical problems. One  reason for the emergence of   MSR  in 2004 was the existence of a new generation of widely-available data mining
algorithms that could scale to interestingly large problems. In this paper,
we pause to reflect on what other kinds of algorithms are widely available and could
be applied to MSR problems.  Specifically, we focus on
{\em search-based software engineering} (SBSE) algorithms. Whereas:
\begin{itemize}
\item
An MSR researcher might deploy a
data miner to learn a model from  data   that predicts for (say) a single target class;
\item
An SBSE researcher might deploy a multi-objective optimizer
to find what {solutions} score best
on multiple target variables.
\end{itemize}

{In other words, both MSR and SBSE share the common goal of providing insights to improve software engineering. However, MSR formulates software engineering problems as data mining problems, whereas SBSE formulates software engineering problems as (frequently multi-objective) optimization problems.}

@@

{The similar goals of these two areas, as well as the intrinsic relationship between data mining and optimization algorithms, has been recently inspiring an} increase in methods that combine MSR and SBSE.
A recent {NII Shonan Meeting}  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) mining software repositories could be improved using {tools from the SBSE community}; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE {algorithms} can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared  resources 
to help more researchers and educators explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/sbse,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
All the materials in this repository
have been used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas.
%\TODO{Re: fig. 1, are we allowed to use Abhaham's nice piece of art?}

@@

The rest of this paper discusses SBSE and its connection to MSR. 
We offer a ``cheats' guide'' to SBSE with just enough information to help researchers and educators use the artifacts in the resource. More specifically, the contributions of the paper are:
\begin{itemize}[leftmargin=*]
    \item To show that optimization (SBSE) and learning (MSR) goes hand in hand (Section~\ref{sec:why}),
    \item Provide resources to seed various research (Section~\ref{sec:scenarios}),
    \item Provide teaching resources, which can be used to create DSE courses (Section~\ref{sec:scenarios}),
    \item Based on our experience, various strategies which can be used to make these DSE techniques more efficient (Section~\ref{sec:guide}), and
    \item List of open research problems to seed further research in this area (Section~\ref{sec:open}). 
\end{itemize}

@@

\begin{figure*}
        \centering
        \small
        \colorbox{gray!10}{
            \begin{tabular}{@{}p{3cm}p{6cm}p{8.35cm}@{}}
                \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Problems in Search-based Software Engineering}}} \\ 
                \multicolumn{3}{c}{
                		\begin{minipage}[b]{0.33\linewidth}
                			\begin{flushleft}
                				\includegraphics[height=4.5cm]{doc/tex/msr18/img/pareto.png}
                				\vspace{8pt}
                			\end{flushleft}
                		\end{minipage}\hspace{0.1cm}
                		\begin{minipage}[b]{0.63\linewidth}
                		        \textbf{Problem: } SBSE converts a SE problem into an optimization problem, where the goal is to find the maxima or minima of objective functions {$y_i=f_i(x)$, $1 \leq i \leq m$, where  $f_i$ are the objective / evaluation functions, $m$ is the number of objectives,} x is called the \textit{independent variable}, and $y_i$ are the \textit{dependent variables}.\\
                		        \textbf{Global Maximum/Minimum: } For single objective ($m=1$) problems, algorithms aim at finding a single solution able to optimize the objective function, i.e., a global maximum/minimum. \\
                		        \textbf{Pareto Front: } For multi-objective ($m>1$) problems, there is no single `best' solution, but a number of `best' solutions. The best solutions are {non-dominated solutions} found using a \textit{dominance} relation.\\
                		        \textbf{Dominance: }The domination criterion  can be defined as: ``A solution $x_1$ is said to dominate\\
                                another solution $x_2$, if $x_1$ is no worse than $x_2$ in all objectives
                                and $x_1$ is strictly better than $x_2$ in at least one objective.'' A solution is called non-dominated if no other solution dominates it.\\
                		        \textbf{Actual {Pareto Front} (PF): } A list of best solutions of a space is called Actual PF ($a\in A$). As this can be unknowable in practice or prohibitively expensive to generate, it is common to take from the union of all optimization outcomes all non-dominated solutions and use it as the (approximated) PF.\\ 
                		        \textbf{Predicted PF: } The solutions found by {an optimization} algorithm are called the Predicted PF ($p\in P$).
                		\end{minipage}
                } \\ 
                \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Components of Meta-heuristic Algorithms (search-based optimization algorithms such as NSGA-II~\cite{deb2000fast}, SPEA2~\cite{zitzler2001spea2}, MOEA/D~\cite{zhang2007moea}, AGE~\cite{wagner2015age})}}} \\
                \multicolumn{3}{c}{
                \begin{minipage}[b]{\linewidth}
                \vspace{0.1cm}
                % \TODO{I'm not sure how useful it is to explain the components here if we don't show the pseudocode of an algorithm, as the persons who don't know the components will not know the pseudocode either, and will thus be unable to understand. Perhaps we can eliminate the plot from the previous section of this figure and add a figure with a general meta-heuristic pseudocode here?}
                \begin{wrapfigure}{r}{0.4\textwidth}
                \includegraphics[height=4.8cm]{doc/tex/msr18/img/sbse_code.png}
                \end{wrapfigure}
                \textbf{Data Collection or Model building: } SBSE process can either rely on a model, which represent a software process~\cite{boehm1995cost} or can be directly applied to any software engineering problem including problems which require evaluating a solution by running a specific benchmark~\cite{krall2015gale}.

                \textbf{Representation: } {This defines how solutions $x$ are represented internally by the algorithm.
                Examples of representations are Boolean or numerical vectors, but more complex representations are also possible. The space of all values that can be represented is the} \textit{Decision Space}.
                % The representation of these solutions is significant to generate the landscape of the problem.

                \textbf{Population: } A set of solutions maintained by the algorithm using the representation.

                \textbf{Initialization: } The process of search {typically} starts by creating random solutions (valid or invalid)~\cite{saber2017seeding, chen2017beyond, chen2017sampling, henard2015combining}.

                \textbf{Fitness Function: } A fitness function maps the solution (which is represented using numerics) to a numeric scale (also called as \textit{Objective Space}) which is used to distinguish between good and not so good solutions. This measure is a domain-specific measure (single objective) or measures (multi-objective) which is useful for the practitioners.
                Simply put fitness function is a transformation function which converts a point in the decision space to the objective space.

                \textbf{Operators: } {These are operators that (1) generate new solutions based on one (e.g., mutation operator) or more (e.g., crossover or recombination operators) existing solutions, and (2) operators that select solutions to pass to the aforementioned operators or to survive for the next iteration of the algorithm. The operators (2) typically apply some pressure towards selecting better solutions either deterministically (e.g., elitism operator) or stochastically.} 
                % \TODO{If space allows, we can mention survival of the fittest.} % They can be used along with an}\TODO{I haven't finished this change yet. I have to come back later.} 
                \textit{elitism operator} simulates the `survival of the fittest' strategy, i.e., eliminates not so good solutions thereby preserving the good solutions in the population.

                \textbf{Generations: } {A meta-heuristic algorithm iteratively improves the population (set of solutions) iteratively. Each step of this process, which includes generation of new solutions using recombination of the existing population and selecting solutions using the elitism operator, is called a generation.  Over successive generations, the population `evolves' toward an optimal solution.}
                \end{minipage}\hspace{0.1cm}
                }
                 \\
                \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Performance Measures (Refer to \cite{wang2016practical,chand2015manyemo} for more detail)}}} \\ 
                % \multicolumn{2}{c}{\textbf{SA}} & \textbf{SBSE} \\ \midrule
                \multicolumn{3}{c}{
                        \begin{minipage}[b]{0.33\linewidth}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/gd.png}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/igd.png}\\
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/hv.png}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/spread.png}
                                \vspace{0.5cm}
                        \end{minipage}
                        \begin{minipage}[b]{0.67\linewidth}
                            \vspace{0.1cm}
                            For single objective problems, measures such as \textit{absolute residual} or \textit{rank-difference} can be very useful and cannot be used for multi-objective problems. The following are the measures used for such problems.\\
                            \textbf{Generational Distance: } Generational distance is the measure of convergence---how close is the predicted Pareto front is to the actual Pareto front. It is defined to measure (using Euclidean distance) how far are the solutions that exist in $P$ from the nearest solutions in $A$. In an ideal case, the GD is 0, which means the predicted PF is a subset of the actual PF. Note that it ignores how well the solutions are spread out.

                            \textbf{Spread: } Spread is a measure of diversity---how well the solutions in P are spread. An ideal case is when the solutions in P is spread evenly across the Predicted Pareto Front.

                            \textbf{Inverted Generational Distance: } Inverted Generational distance measures both convergence as well as the diversity of the solutions---measures the shortest distance from each solution in the Actual PF to the closest solution in Predicted PF. Like Generational distance, the distance is measured in Euclidean space. In an ideal case, IGD is 0, which means the predicted PF is same as the actual PF.

                            \textbf{Hypervolume: } Hypervolume measures both convergence as well as the diversity of the solutions---hypervolume is the union of the cuboids w.r.t. to a reference point. Note that the hypervolume implicitly defines an arbitrary aim of optimization. Also, it is not efficiently computable when the number of dimensions is large, however, approximations exist.

                            \textbf{Approximation: } Additive/multiplicative Approximation is an alternative measure which can be computed in linear time (w.r.t. to the number of objectives). It is the multi-objective extension of the concept of approximation encountered in theoretical computer science. 
                            % The intuition is that the search process aims at finding a set of solutions with a small approximation ratio, so why not simply compute the approximation ratio (as?

                        \end{minipage}	
                }
            \end{tabular}
        }
        \caption{A {brief} tutorial on Search-based Software Engineering.}
        \label{fig:sbse_crash}
\end{figure*}

\begin{figure*}[t]
    \centering
    \small
    \begin{tabular}{@{}p{3cm}p{6cm}p{8.35cm}@{}}

                % \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{}}} \\ 
                \rowcolor{gray}\textcolor{white}{\textbf{Features}} & \hspace{2cm}\textcolor{white}{\textbf{MSR}} & \hspace{3cm}\textcolor{white}{\textbf{SBSE}} \\ 
                 \rowcolor{gray!30} \textbf{Primary inference} & Induction, summarization, visualization & Optimization \\
                \textbf{Inference speed} & Very fast, scalable & Becoming faster, more scalable\\
                 \rowcolor{gray!30}\textbf{Data} often collected &
                 Once,  then processed.
                &
                On-demand
                from  some model---which means an SBSE analysis can 
                generate new samples of the data in very  specific regions.
                \\ 
                \textbf{Conclusions} often 
                generated via
                &
                A single  execution of a data miner or an ensemble, 
                perhaps after some data pre-processing. 
                &
                An evolutionary process  where, many times, execution $i+1$ is guided
                by the results of execution $i$.
                \\

                 \rowcolor{gray!30}\textbf{Canonical   tools} are usually
                &
                Data mining algorithms like  the decision
                tree learners of WEKA~\cite{hall2009weka} or the mathematical modeling tools of R~\cite{rmanual18} or Scikit-learn~\cite{scikit-learn}.
                &
                {Search-based} optimization algorithms which may be either home-grown scripts or parts of large toolkits such as jMETAL\cite{refs2jmetalDEE}, Opt4j~\cite{opt4jpaper}, DEAP~\cite{DEAP_JMLR2012}.
                \\ 
                \textbf{Canonical   problems}
                &
                Defect prediction~\cite{lessmann2008benchmarking}   or Stackoverflow text mining~\cite{fu2017easy}. 
                &
                Minimizing a test suite~\cite{fraser2007redundancy}, configuring a software system~\cite{nair2017faster} or extracting a valid products from a product line description~\cite{sayyad13b}.
                % or selecting screen designs that
                % reduce the power consumption  mobile devices
                \\

@@

 \begin{figure}[b]
\small

\item
Mission-critical systems are risk averse and may accept very high false alarm rates,
just as long as they catch any life-threatening possibility. That is, such projects
do not care about effort- they want to {\em maximize recall} regardless of any impact
that might have on the false alarm rate.
\item  Suppose a new hire wants
 to impress their manager. That
 new hire might want to ensure that no result presented to  management contains  true negative;
i.e. they wish to {\em maximize precision}.
\item
Some communities do not care about   low precision,
just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction
{\em selectivity} and offer an
extensive discussion of the merits of this measure~\cite{hayes06}.
\end{enumerate}
\\ \hline
\rowcolor{gray!10}
Beyond defect prediction are other goals that combine defect prediction with other economic
factors:
\begin{enumerate}[leftmargin=0.4cm]
\setcounter{enumi}{3}
\item
Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
that contain the most bugs.
\item In other work, Lumpe et al. are concerned about
 {\em amateur  bug fixes}
%  ; i.e. those that made by programmers to regions of the code that are unfamiliar, to them
~\cite{me11f}.
Such amateur fixes are highly correlated to errors and, hence, to
avoid such incorrect bug fixes, we have to optimize
for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
\item In {\em better-faster-cheaper} setting, one seeks  project changes that lead
to fewer defects and faster development times using fewer resources~\cite{elrawas10,me07f,me09a,me09f}.
\item
Sayyad~\cite{sayyad13a,sayyad13b} explored models of software product
lines whose value propositions are defined by five objectives.
\end{enumerate}
\\ \hline
\rowcolor{gray!10}
All the above measures relate to the tendency of a predictor to find something. Another measure could be {\em variability} of predictor.
\begin{enumerate}[leftmargin=0.4cm]
\setcounter{enumi}{7}
\item
In their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{mockus09}.
\end{enumerate}\\\hline
\end{tabular}
\caption[Different users value different things.]{Different users value different things.
% Technical note:  some of
% these goals are defined in terms of
% Figure~\ref{fig:criteria}.
}\label{fig:goals}
\end{figure}

@@

\section{  Why? (Synergies of MSR + SBSE)} \label{sec:why}

% If MSR was completely different to SBSE (as suggested by Figure~\ref{fig:sbse_crash}), 
% then there would be no point
% to this paper. This section argues combining both methods is insightful and useful.
